PMV: Which formulation should you use the ISO 7730:2005 or ASHRAE 55:2020?

### 2023-08-31 Manuscript/src/sections/results.tex
paper: updated per-mode units, added bar chart for v>=.2, updated table

\subsection{Comparison of PMV accuracy in predicting thermal sensation}\label{subsec:model-accuracy-comparison-in-predicting-thermal-sensation}
The \ac{pmv} was developed with the primary aim of predicting \ac{tsv}, consequently, we are here comparing the prediction accuracy of the two formulations.
% todo:
%  We can use Toby's or Michael but not both, even, though I like mine more
%  It is hard to notice that these are two distint graph because the legend is moving accross.
%  and have a thin grey line to separate the two group, another option would be to add a light grey background for the two PMV and show that they are distinct.
\begin{figure*}[htb!]
    \centering
    \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants. 
    The number of data points in each bin of the two charts is the same and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart while the model accuracy of predicting participants grouped by their \ac{tsv} is overlayed over each bar. 
    A random model, randomly selecting a thermal sensation vote would have an overall accuracy of \qty{14}{\percent}}
    \label{fig:bar_stacked_model_accuracy}
\end{figure*}
Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
Both \ac{pmv} formulations underestimated the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracy of the \ac{pmv} and \ac{pmv-ce} were \qty{33}{\percent} and \qty{34}{\percent}, respectively.
Being the classification problem unbalanced, the simple accuracy is not an optimal metric to rate the model prediction accuracy since a default strategy of guessing the majority class would lead to a high overall model accuracy.
A model that would have always predicted `neutral' would have achieved an overall accuracy of \var{perc_tsv_neutral}, the number of participants who voted \ac{tsv}=0.
For this reason, in Table~\ref{tab:f1}, we report the F1-scores for all the models.
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}).
% todo:
%  in the table I should also report the F1 scores if I filter out some of the TSV.
%  The PMV model should only be used in the range -2 and 2 so at least we should report also the results in this range.
\begin{table}[htb!]
    \centering
    \input{tables/f1.tex}
    \caption{F1-score for the \ac{pmv} and \ac{pmv-ce} models.}
    \label{tab:f1}
\end{table}

>>>>

\subsection{Comparison of PMV accuracy in predicting thermal sensation}\label{subsec:model-accuracy-comparison-in-predicting-thermal-sensation}
The \ac{pmv} was developed with the primary aim of predicting \ac{tsv}, consequently, we are here comparing the prediction accuracy of the two formulations.
% todo:
%  We can use Toby's or Michael but not both, even, though I like mine more
%  It is hard to notice that these are two distint graph because the legend is moving accross.
%  and have a thin grey line to separate the two group, another option would be to add a light grey background for the two PMV and show that they are distinct.
\begin{figure*}[htb!]
    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0}
        \caption{All data}
     \end{subfigure}
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/bar_stacked_model_accuracy_0.2}
        \caption{Only data with \ac{v} $\geq$ \qty{0.2}{\m\per\s}}
     \end{subfigure}
    \caption{The calculated \ac{pmv} value is grouped by the \ac{tsv} value reported by the participants. 
    The number of data points in each bin of the two charts is the same and this allows us to compare the accuracy of both models.
    The overall prediction accuracy is shown above the chart while the model accuracy of predicting participants grouped by their \ac{tsv} is overlayed over each bar. 
    A random model, randomly selecting a thermal sensation vote would have an overall accuracy of \qty{14}{\percent}.}
    \label{fig:bar_stacked_model_accuracy}
\end{figure*}
Being \ac{tsv} the value reported by participants (i.e., ground truth), in Figure~\ref{fig:bar_stacked_model_accuracy} we grouped participants' responses by \ac{tsv} and reported the simple accuracy of the different \ac{pmv} formulations over each sub-figure.
Both \ac{pmv} formulations underestimated the conditions at which participants are thermally dissatisfied with their environment.
The overall accuracy of the \ac{pmv} and \ac{pmv-ce} were \qty{33}{\percent} and \qty{34}{\percent}, respectively.
Being the classification problem unbalanced, the simple accuracy is not an optimal metric to rate the model prediction accuracy since a default strategy of guessing the majority class would lead to a high overall model accuracy.
A model that would have always predicted `neutral' would have achieved an overall accuracy of \var{perc_tsv_neutral}, the number of participants who voted \ac{tsv}=0.
For this reason, in Table~\ref{tab:f1}, we report the F1-scores for all the models.
The F1-macro score, which is free from label imbalance, depicts that the accuracy of both models across all metrics is marginally better than random guessing (i.e., \qty{14}{\percent}).
% todo:
%  in the table I should also report the F1 scores if I filter out some of the TSV.
%  The PMV model should only be used in the range -2 and 2 so at least we should report also the results in this range.
\begin{table}[htb!]
    \centering
    \input{tables/f1.tex}
    \caption{F1-score for the \ac{pmv} and \ac{pmv-ce} models.}
    \label{tab:f1}
\end{table}
